\documentclass[11pt,fleqn]{article}

\newcommand{\indentpar}{\phantom{=}}
\newcommand{\bli}{\begin{itemize}}
\newcommand{\eli}{\end{itemize}}

\begin{document}

    %% Title Page %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{center}

        {\large \textbf{Soil Settlement Analysis Software}}\\[2mm]
        {\large \textbf{VDispl}}\\[2mm]
        {\large \textbf{Spring 2022}}\\[8mm]
        {\huge \textbf{Inconsistencies in Settlements Textbook and FORTRAN Code}}\\[6mm]
        {\large \textbf{Dr.~Spencer Smith, Emil Soleymani}}\\[2mm]
        {\large \textbf{McMaster University}}\\[6mm]
        {\large Revised: May 9, 2022}
      
      \end{center}
      
      \medskip

      % Description
      \indentpar During review of the legacy FORTRAN code for the VDispl software, 
      we referenced the Settlements Analysis book linked in the README 
      file in order to correlate each calculation with its corresponding 
      theories and formulas. This process revealed many potential errors 
      in the code and the formulas presented in the textbook, along with 
      some inconsistencies between calculations made in the code and 
      calculations shown in the textbook. This document is a compilation 
      of all such occurrences.
      
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    
    \pagebreak
    
    %% Notes %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section*{Notes}
    \indentpar All references to FORTRAN code are relative to line numbers 
    in the \emph{most recent} version of the code, found under 
    \textbf{Resources/fortran\_src/vdisp.for} while all references to the pages
    in the Settlements Analysis textbook refer to a page number of the PDF linked 
    in the README.md file.

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    
    \medskip

    %% Errors in Textbook %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \section*{Potential Errors in Textbook}
    \indentpar Having examined the many formulas in the book during the research and 
    analysis of the FORTRAN code, we have come across some potential errors in the
    textbook, ranging from variable names to questionable units.
    \subsection*{Units for unit weight of water, $\gamma_w$:} 
    \indentpar On page 12 of the Settlements Analysis PDF, 
    under heading \(3\), there is a reference to a constant $\gamma_w$, 
    which represents the unit weight of water. This constant is known
    to be 9.807 $kN/m^3$ in SI units, however the textbook lists it as 
    0.031tsf. The unit tsf — tonnes per square foot — seems to be a unit
    of pressure which can be converted to $N/m^2$. We have no current 
    explanation for this discrepancy.
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   
     
\end{document}