\documentclass[11pt,fleqn]{article}

\usepackage{blindtext}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
    }
\urlstyle{same}

\newcommand{\indentpar}{\phantom{=}}
\newcommand{\bli}{\begin{itemize}}
\newcommand{\eli}{\end{itemize}}

\begin{document}

    %% Title Page %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      
      \title{Verification and Validation Plan for VDisp Software}
      \date{May 16th, 2022}
      \author{Emil Soleymani, Dr.~Spencer Smith\\ McMaster University}
      \maketitle

      \medskip

      % Description
      \indentpar In order to verify the validity of the \emph{VDisp} software, we came
      up with various Unit and System tests. The Settlements Analysis textbook (linked in \emph{README.md} 
      file) outlined four very good sample input files, with their expected outputs 
      already displayed. These were the perfect starting points in terms of system tests, however 
      they did not cover many possible input combinations. Thus, we had to come up with many of 
      our own system tests. This document outlines the details of the Unit and System tests
      used to verify the \emph{VDisp} software.
      
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    
    \pagebreak

    %% System Tests %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \section*{System Tests}
    \indentpar We explain the system tests used in the validation and verification
    of the \emph{VDisp} software below.
    \subsection*{Test Input Files from Appendix F}
    \indentpar In Appendix F of the Settlements Analysis Textbook, under section (F-3) 
    on p.171, there are 4 sample input files along with their respective expected outputs.
    We copied these input files, storing them in the directory located at 
    \href{https://github.com/smiths/vdisp/tree/main/test/.testdata}{\emph{“vdisp/test/.testdata”}}.
    We made our \emph{InputParser} module parse each of these files, making sure no errors arose and 
    that each piece of data was parsed correctly. The test cases can be found in the 
    \href{https://github.com/smiths/vdisp/tree/main/test/runtests.jl}{\emph{runtests.jl}} file.
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}